---
title: "Your Project Title (be descriptive and creative!)"
author: "Team members names, tutorial groups, and group number (if applicable)"
subtitle: "You can either put a subtitle here, or delete this line"
date: April 1, 2021
fontsize: 10pt
output: 
  beamer_presentation:
    theme: "Pittsburgh"
    colortheme: "orchid"
    fonttheme: "structurebold"
    slide_level: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.pos = "H", fig.height=3, fig.width=4)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# echo=FALSE will stop the code chunk from appearing in the knit document
# warning=FALSE and message=FALSE will stop R messages from appearing in the knit document
library(tidyverse)

# here is the data for this project
RCYC <- read_csv("STA130_project_data.csv")


# see the project information page for more information:
# https://q.utoronto.ca/courses/206597/pages/project-overview-2?module_item_id=2274626
```


## Question 1
**What is the correlation between a member's age and sex and the total amount they spent at RCYC facilities?**  
\textbf{Motivation}: our goal is to help better adapt \textsc{rcyc}`s facilities to the members' needs. Then, the first research question...  

 - explores whether age, sex, or both can predict a member's spending  
 - can reveal interesting patterns in spending
 
### How does this help?
Based on these data, the managers of \textsc{rcyc} can make an informed decision on which facilities to invest in more

 - perhaps in combination with other available, external data, such as an age group's preferred activities.  
 - for instance, if there is a correlation between age and spending, the managers can decide whether to focus efforts on retaining old members or recruiting new members, depending on the trend. 

## Statistical methods
To analyze the relationship, we use a linear regression model with two interacting predictors. We assume the conditions---linearity of relation, constance of variance, independence of observation, and normality of residuals. Also, we create a column called `total_spending`---the sum of the separate accounts---and filter for 2017 values.

### Model 
\[y_i = \beta_0 + \beta_1 x_{1i} + \beta_2x_{2i} + \beta_3x_{1i}x_{2i} + \varepsilon_i \]
Where \(y_i\) is the predicted total spending in 2017, \(x_{1i}\) is the age of the member, \(x_{2i}\) is the sex of the member---where \(0\) is female and \(1\) is male.

### Hypotheses
Let \(\alpha = 0.05\). \[H_0 : \beta_1 = \beta_2 = \beta_3 = 0 \qquad H_A: \text{at least one } \beta_i \neq 0\]
In simple terms, unless the data shows otherwise, we expect that there is no linear relationship between age and spending or sex and spending. 

---
```{r fig.cap="\\label{fig:asspending} Relationship between member's age, sex, and total spending (2017)", fig.width=6.3, fig.height=4.5}
augmented_rcyc <- RCYC %>% 
  mutate(total_spending = city_dining + island_dining + bar_spending + other_spending) %>%  # create a new variable containing total spending
  filter(year == 2017 & !is.na(Age) & !is.na(Sex) & !is.na(other_spending)) %>%  # filter the data such that only entries from 2017, and contains information, are included
  select(Age, Sex, total_spending)  # since we don't need more

augmented_rcyc %>% ggplot(aes(x=Age, y=total_spending, color=Sex)) +  # plot the data where total_spending ~ Age * Sex
  geom_point(alpha=0.2) + 
  geom_smooth(formula = y ~ x, method="lm", se=FALSE) +
  labs(x="Age", y="Total spending")

# model <- lm(total_spending ~ Age, data=augmented_rcyc)
# summary(model)$coefficients
# model <- lm(total_spending ~ Sex, data=augmented_rcyc)
# summary(model)$coefficients
# model <- lm(total_spending ~ Age * Sex, data=augmented_rcyc)
# summary(model)$coefficients
# 
# 
# model <- lm(total_spending ~ Age, data=augmented_rcyc)
# summary(model)$r.squared
# model <- lm(total_spending ~ Sex, data=augmented_rcyc)
# summary(model)$r.squared
# model <- lm(total_spending ~ Age * Sex, data=augmented_rcyc)
# summary(model)$r.squared
```

<!-- This document shows a few basics on making slides with R markdown. -->

<!-- To produce the slides, Knit to PDF (Beamer). -->

<!-- --- -->

<!-- Three dashes starts a new page when it is not started by a new header. If you want to put a gap between parts of a slide `\vspace{0.3cm}` will do it. You can change the number inside the curly brackets to get a smaller or larger gap. -->

<!-- \vspace{0.8cm} -->

<!-- ### This is a heading that doesn't start a new page but makes a nice emphasis box -->

<!-- You can make text **bold** or in *italics*. -->

<!-- To make bullet points, start the points after a blank line: -->

<!-- - point one -->
<!-- - another point -->

<!-- ## Markdown has nice formatting options for you -->

<!-- 1. Check out the cheat sheet [https://github.com/rstudio/cheatsheets/raw/master/rmarkdown-2.0.pdf](https://github.com/rstudio/cheatsheets/raw/master/rmarkdown-2.0.pdf) -->
<!--     i) Oh look! A sub-item in the list (note two 'tabs' before this line) -->
<!-- 2. You can get help making tables here: [https://www.tablesgenerator.com/markdown_tables#](https://www.tablesgenerator.com/markdown_tables#) -->

<!-- | A column header | Another column header                | -->
<!-- |-----------------|--------------------------------------| -->
<!-- | First row       | First row, but now the second column | -->

<!-- ### You can also use LaTeX commands -->
<!-- Roses are \textcolor{red}{red}, violets are \textcolor{blue}{blue}. -->
<!-- - column layouts -->
<!-- - font size for specific bits -->
<!-- - centering -->
<!-- - equations, inline or not inline e.g. equation of a line and and subsscprits like H_0 -->

<!-- --- -->

<!-- Include some R output -->

<!-- ```{r} -->
<!-- ggplot(cars, aes(x=speed, y=dist)) + -->
<!--   geom_point() -->
<!-- ``` -->

<!-- --- -->

<!-- Include the output without showing the code and R messages (which is what you want for your poster presentation).  This R code chunk also changes the size of the plot. -->

<!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=3, fig.width=4} -->
<!-- ggplot(cars, aes(x=speed, y=dist)) + -->
<!--   geom_point() -->
<!-- ``` -->

<!-- This plot shows that there is a positive relationship between distance and speed. -->

<!-- ## Read more -->

<!-- For more on creating an `beamer` presentation see [https://bookdown.org/yihui/rmarkdown/beamer-presentation.html](https://bookdown.org/yihui/rmarkdown/beamer-presentation.html) -->

<!-- You can change the style, colours and fonts in your presentation by picking from a library of available themes. Once you find ones you like, you change the settings in the YAML section at the top of this RMarkdown document. -->
<!-- [http://deic.uab.es/~iblanes/beamer_gallery/index.html](http://deic.uab.es/~iblanes/beamer_gallery/index.html) -->


<!-- # Headings you should include in your project -->

<!-- ## Introduction -->

<!-- Include here a few sentences to introduce the problem and provide context. You might want to briefly summarize the data in words (what is the data and what is it used for). You can present the questions you are investigating here.  -->

<!-- ## Objectives (optional) -->

<!-- You can list the questions of interest in complete English sentences here to highlight them.  -->

<!-- ## Data Summary (optional) -->

<!-- Here you can explain how you cleaned the data and created variables suitable for answering your questions.  -->
<!-- You can also include graphical displays that either motivated or address the questions. -->

<!-- ## Statistical Methods -->

<!-- Describe here what you have done to the data without presenting any results (output). If you want to indicate variables by symbols or variable names, define them here.  -->

<!-- ## Results -->

<!-- Present the main results here, in order of importance, related to the questions asked. You might use tables or graphs, or other ways to summarize your results. -->

<!-- ## Conclusion -->

<!-- Give your main conclusions here. Follow the order of questions you presented.  -->

<!-- Here you can also mention any additional considerations, concerns, or issues you might have. For example, if the results were unexpected, you can discuss this and perhaps offer possible explanations. -->

<!-- ## References and Acknowledgements (optional) -->

<!-- If you received any help from someone other than your team members you can acknowledge them. For example:    -->
<!-- *The authors would like to thank "TA name" for helpful suggestions and comments that improved the presentation of this poster.* -->


